\thetitle

### 2021-03-03 writing/rational-natural.tex
removing wes

To account for this situation, we devise a new mode of the Natural rational
programmer that follows a migration process based on exceptions:
\begin{quote}
\it A {\em Natural exception trail\/} is a sequence of scenarios $\conf_0,...\conf_n$ of a
program $\system$ such that for all $0 \leq i \leq n - 1$, $\conf_i \subset
\conf_{i+1}$ and $\conf_{i+1} \setminus \conf_i = \{\exception{\system, \conf_i}\}$
where $\exception{\system, \conf}$ denotes the location of the exception of $\conf$.
\end{quote}

Same as for success for a Natural blame trail, we define success for a
Natural exception trail.
Putting the definitions for the two modes together, we can now compare the usefulness of blame 
with that for mere exceptions for debugging a scenario in the context of Natural semantics.
\begin{quote}
\it 
  Given a program $\system$ and a root $\conf_0$ in $\lattice{\system}$,
  Natural blame is \emph{more useful} than Natural exceptions for
  debugging $\conf_0$ iff 
  the Natural blame trail 
  that starts at $\conf_0$ is successful while the Natural exception trail that
  starts at $\conf_0$ is failing.
\end{quote}

>>>>

To account for this situation, a new mode of the Natural rational
programmer follows a migration process based on exceptions:
\begin{quote}
\it A {\em Natural exception trail\/} is a sequence of scenarios $\conf_0,...\conf_n$ of a
program $\system$ such that for all $0 \leq i \leq n - 1$, $\conf_i \subset
\conf_{i+1}$ and $\conf_{i+1} \setminus \conf_i = \{\exception{\system, \conf_i}\}$
where $\exception{\system, \conf}$ denotes the location of the exception of $\conf$.
\end{quote}

The definition of success for a Natural exception trail follows that for
a Natural blame trail.
Together the definitions for the two modes allow the comparison of the usefulness of blame 
with that for mere exceptions for debugging a scenario in the context of Natural semantics.
\begin{quote}
\it 
  Given a program $\system$ and a root $\conf_0$ in $\lattice{\system}$,
  Natural blame is \emph{more useful} than Natural exceptions for
  debugging $\conf_0$ iff 
  the Natural blame trail 
  that starts at $\conf_0$ is successful while the Natural exception trail that
  starts at $\conf_0$ is failing.
\end{quote}

### 2021-03-03 writing/results.tex
removing wes

We run the experimental process from section~\ref{sec:rational} on the
sampled debugging scenarios from section~\ref{sec:sample} using a machine with two Intel Xeon Gold 6258R processors (28 doubly-threaded cores each) and 500GB of memory.
Each debugging scenario had a 4 minute timeout and a
memory limit of 6GB. The complete experiment required
over 30,000 compute hours.

@@

Figure~\ref{fig:success-bars} summarizes the overall success rates of every mode.
The success rates illustrate a few points that underly the rest of our analysis.
The first notable piece of information from
this figure is that every mode has failed debugging scenarios, not just
Erasure. This should
not come as a surprise to the astute
reader. After all, as we
discuss above, some modes are more successful than others in certain
scenarios. Indeed any mode can fail if no untyped module from the program is identified in the error.
For example, running a scenario may result in an
exception that carries no useful information about which
module the programmer should type next, e.g. because the stack trace
does not contain frames from any module of the program, or only typed modules. This situation
can happen at any point along a blame trail (figure~\ref{fig:effort-table} dives into this below), causing it to fail.

@@

In Transient, similar to Natural,
most failures are due to unhelpful exception information (1851 for both
Transient first and last blame).  
However, Transient also has a substantial
number of failures because scenarios hit the time and memory
limits of our experiment (\textasciitilde770 scenarios).  Additionally, there are nearly 1,000 cases where
Transient reports an empty blame set, leaving the rational programmer
without hints about how to proceed.
In section~\ref{sec:threat:transient}, we discuss how both of these causes of
failure for Transient affect our experiment.

>>>>

The experimental process from section~\ref{sec:rational} was run on the
sampled debugging scenarios from section~\ref{sec:sample} on a machine
with two Intel Xeon Gold 6258R processors (28 doubly-threaded cores each)
and 500GB of memory.  Each debugging scenario had a 4 minute timeout and a
memory limit of 6GB. The complete experiment required over 30,000 compute
hours.

@@

Figure~\ref{fig:success-bars} summarizes the overall success rates of every mode.
The success rates illustrate a few points that underly the rest of our analysis.
The first notable piece of information from
this figure is that every mode has failed debugging scenarios, not just
Erasure. This should
not come as a surprise to the astute
reader. After all, as
discussed above, some modes are more successful than others in certain
scenarios. Indeed any mode can fail if no untyped module from the program is identified in the error.
For example, running a scenario may result in an
exception that carries no useful information about which
module the programmer should type next, e.g. because the stack trace
does not contain frames from any module of the program, or only typed modules. This situation
can happen at any point along a blame trail (figure~\ref{fig:effort-table} dives into this below), causing it to fail.

@@

In Transient, similar to Natural,
most failures are due to unhelpful exception information (1851 for both
Transient first and last blame).  
However, Transient also has a substantial
number of failures because scenarios hit the time and memory
limits of our experiment (\textasciitilde770 scenarios).  Additionally, there are nearly 1,000 cases where
Transient reports an empty blame set, leaving the rational programmer
without hints about how to proceed.
Section~\ref{sec:threat:transient} explains how both of these causes of
failure for Transient affect our experiment.
